Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-04-13 TEBenchmarkPaper/article.tex
TEB: Better motivation

% Lay out the field of TE: motivation, tools, evaluation, problems...
% FIXME: Strengthen motivation:
%  - Automated Scientific Discovery (e.g. Dundee drug discovery "centaur" story)
%  - "Mixed initiative" (social machine?); maybe Kasparov
%  - Gowers calling for better AI in maths

@@

This has applications wherever we find uses for formal methods: in proof
assistants and their libraries, in mathematics education and research, and in
the specification and verification of software. Although formal methods, and
automated reasoning more generally, have been advocated in mathematics (notably
by Voevodsky~\cite{voevodsky2010univalent} and
Gowers~\cite{ganesalingam2013fully}) and software engineering (for example via
dependently-typed
programming~\cite{McKinna:2006, chlipala2011certified, Xi2003}), they have a
reputation for being difficult and expensive, which has historically limited
their use to high-assurance domains such as aerospace and microprocessor design.
Increased automation is one way to address these problems, and conjecture
generation has already been shown to aid in specification and verification of
software properties~\cite{Claessen.Johansson.Rosen.ea:2013}).

Similar tasks are also studied in the domain of Computational \emph{Scientific}
Discovery~\cite{king2004functional,Williams20141289,schmidt2009distilling},
although that relies on inductive reasoning and experimental testing which (in
principle) are not so important for pure mathematics. Whilst we \emph{have}
found these methods to also be important for MTE tools (in particular for the
\emph{plausibility} of generated conjectures), we leave a more thorough
application of our results to scientific reasoning for future work.

Even limiting ourselves to mathematics applications, it is difficult to measure
and compare the success of approaches and tools. This is partially due to their
diversity, but also because of the inherent ambiguity of the task, the different
goals emphasised by their designers and the variety of evaluation methods
employed. We attempt to solve this discrepancy, at least for the foreseeable
future, by defining a standard, unambiguous benchmarking approach with which to
compare the conjecture generation of MTE tools. Our contributions include:

>>>>

% Lay out the field of TE: motivation, tools, evaluation, problems...
% FIXME: Strengthen motivation:
%  - Automated Scientific Discovery (e.g. Dundee drug discovery "centaur" story)
%  - "Mixed initiative" (social machine?); maybe Kasparov

@@

This has applications wherever we find uses for formal methods: in proof
assistants and their libraries, in mathematics education and research, and in
the specification and verification of software. Although formal methods, and
automated reasoning more generally, have been advocated in mathematics (notably
by Voevodsky~\cite{voevodsky2010univalent} and
Gowers~\cite{ganesalingam2013fully}) and software engineering (for example via
dependently-typed
programming~\cite{McKinna:2006, chlipala2011certified, Xi2003}), they have a
reputation for being difficult and expensive, which has historically limited
their use to high-assurance domains such as aerospace and microprocessor design.
One way to reduce these hurdles is to increase automation, which in the case of
software verification can benefit from the introduction of conjecture generation
tools~\cite{Claessen.Johansson.Rosen.ea:2013}. Another approach is to tailor the
division of labour between humans and machines such that each is playing to
their strengths, which has been referred to as ``centaur
teams''~\cite{harari2017reboot, davenport2015beyond}. In this respect a
conjecture generating tool can search a much larger space of relationships than
a human, whilst leaving the ultimate judgement of which to investigate in more
detail to the user.

Similar tasks are also studied in the domain of Computational \emph{Scientific}
Discovery~\cite{king2004functional,Williams20141289,schmidt2009distilling}, for
example searching for new drugs. The major difference between scientific and
mathematical discovery is that inductive reasoning and experimental testing are,
in principle, more important for the former, although we note that they are also
core principles in the mathematical tools we have investigated (in particular
for ensuring the \emph{plausibility} of conjectures).

We limit ourselves to applications in mathematics, but even here it is difficult
to measure and compare the success of approaches and tools. This is partially
due to their diversity, but also because of the inherent ambiguity of the task
(what counts as ``interesting''?), the different goals emphasised by their
designers and the variety of evaluation methods employed. We attempt to solve
this discrepancy, at least for the foreseeable future, by defining a standard,
unambiguous benchmarking approach with which to compare the conjecture
generation of MTE tools. Our contributions include:
